What's in a Domain? Anaylsis of URL Features

### 2022-10-03 paper/paper.tex
Paper update
Removing debug prints, bug fixes, preparing for experiments. Release 0.3.0

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as the primary feature.
The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
These 3 URL classification problems are summarised in Table \ref{tab:data}

The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
with \cite{Pazzani1996}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
Malware              &46,944          &2       &            \\
Phishing             &45,343          &2       &            \\
WebKb 4Uni           &8,284           &7       &            \\
DMOZ                 &8,284           &7       &            \\
Syskill \& Webert     &8,284           &7       &            \\
\bottomrule
\end{tabular}
\end{table}

We generate all url features for each of these datasets and then apply a range of machine learning
techniques to build an appropriate classifier.

@@

@@

>>>>

The data used in this study was colated from a range of publications that 
present internet classification problems containing URLs as the primary feature.
The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
with a human generated categorisation for determining personal preferences in webpage
content\cite{Pazzani1996}. These 4 URL classification problems are summarised in Table \ref{tab:data}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
Malware              &46,944          &2       &75\%        \\
Phishing             &45,343          &2       &78\%        \\
WebKb 4Uni           &8,284           &7       &45\%        \\
Syskill \& Webert    &330             &3       &68\%        \\
\bottomrule
\end{tabular}
\end{table}

We generate all url features for each of these datasets and then apply a range of machine learning
techniques to build classifiers that can be analysed for key features for each task.

@@

\begin{table}
\caption{Machine Learning Results}
\label{tab:results}
\begin{tabular}{|l|r|r|r|r|}
\toprule
Dataset              &NB     &LR    &XT    &LGBM     \\
\midrule
Malware              &-      &-     &-     &-        \\
Phishing             &-      &-     &-     &-        \\
WebKb 4Uni           &-      &-     &-     &-        \\
Syskill \& Webert    &-      &-     &-     &-        \\
\bottomrule
\end{tabular}
\end{table}

@@

We have described the structural elements of a URL from which context specific features can be extracted.
These feature ideas tend to be used indepednetly within different domains. In this paper we have have 
collated them into an open source URL feature generation package and then compare their utility across a range
of indepenent tasks. We have observed that the various structural regions play different roles across 
these tasks, exhibiting varying levels of importance.
